---
title: "Solution for Homework 1"
author: "Jacky Tao"
date: 2022-09-15
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
```

# Problem 1

Load the `penguins` dataset first.

```{r}
data("penguins", package = "palmerpenguins")
```

Then, let's describe the dataset!

Here's the summary of the dataset.

```{r}
summary(penguins)
```

I think `species`, `island` are important qualitative variables, and `flipper_length_mm`, `body_mass_g` are important quantitative variables.

The dataset has `r nrow(penguins)` rows and `r ncol(penguins)` columns.

The mean flipper length is `r round(mean(penguins$flipper_length_mm,na.rm = TRUE),2)` mm.

Make a scatterplot of `flipper_length_mm`(y) vs `bill_length_mm`(x).

```{r, warning = FALSE}
ggplot(data = penguins,
       aes(x = bill_length_mm,
           y = flipper_length_mm)) + 
  geom_point(aes(color = species,
                 shape = species))
```

Export my scatterplot.

```{r, warning = FALSE, message = FALSE}
ggsave("p8105_hw1_jt3386_scatterplot.pdf")
```

# Problem 2
